\documentclass[a4paper,11pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge   \textsc{Ricardo Apú Chinchilla}
	}\bigskip\par}

%--------------------SECTIONS-----------------------------------
\section{Summary}


ADHD kid turned programmer, mostly focused in databases and backend oriented work. I have used Java, Python, Javascript(Node) and even some Go to create and mantain APIs and Data Pipelines. I have helped design and maintain relational databases in MS-SQL, Postgres, MySQL and non relational ones in MongoDB, Cassandra and Firebase. I also have decent experience with building and supporting React components and sites.

I pride myself in asking lots of questions and really striving to understand my client's goals to align  with them and get the best work experience possible for everyone. 

\section{Personal Information}

\begin{tabular}{rl}
    \textsc{Mobile:}     & +506 87508165\\
    \textsc{email:}     & \href{mailto:ricardoapuch@gmail.com}{ricardoapuch@gmail.com}\\
    
\end{tabular}

%Section: Work Experience at the top
\section{Work Experience}
\begin{enumerate}
    \item \textbf{2020-2023 Gorilla Logic} \emph{Full Stack \& Data Engineer} \\
    Design and Fullstack development of social media app for hospital workers.\\
    Sequelize. Typescript. Postgres. React. \\
    Development and support of pipelines migrating data from competitors in webapp with Django and Postgres.
    Development and support of data ingest and clense python jobs for three-tiered Databricks Datalake.  \\ 
    Python. Pyspark. Airflow. Astronomer. ETL. 
    \item \textbf{2019-2020 EY}   \emph{Fullstack Blockchain Developer} \\
    Fullstack development  of app on the Ethereum blockchain. Implementation of ZKP (Zero-Knowledge Proofs) in private blockchain. \\
    ExpressJS. Prisma. MongoDB. Postgres. React. Solidity. TruffleGanache. Docker. Docker Compose.
    \item \textbf{2016-2019 Independent} \emph{Software Consultant} \\
    Transactional Database support and design, RESTful APIs \& data migrations. Frontend development in Android and PC.\\
    MSSQL. Postgres. MySQL. MariaDB. Cassandra. Java 8. Java EE. REST. Hibernate. Persistence API. Android. Kotlin. Firebase. \\
\end{enumerate}

%Section: Education
\section{Education}
\begin{tabular}{lll}\\
 \textsc{20014-2018} \quad & Bachelor in  \textsc{Computer Science} \quad& \textbf{Universidad de Costa Rica}\quad\\
\end{tabular}\\

%Section: Languages
\section{Languages}
\begin{tabular}{lll}\\
\textsc{Spanish:} Native \quad &\textsc{English:} C2 \quad &\textsc{German\&French:} Basic\quad \\
\end{tabular}\\
\vspace{5mm} %5mm vertical space
\end{document}
